Comb associative operads

### 2018-08-27 Article.tex
Maj abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We study quotients of the magmatic operad, that is the free
  nonsymmetric operad over one binary generator. In the linear setting,
  we show that the set of these quotients admits a lattice structure and
  we show the Grassmann formula for this lattice. In the nonlinear
  setting, we define comb associative operads, indexed by nonegative
  integres, as generalizations of the associative operad. We show that
  the set of comb associative operads admits a lattice structure,
  isomoprhic to the lattice of nonnegative integers equipped with the
  division order, and we provide a finite convergent presentation for the
  comb associative operad corresponding to $3$. Finally, we study
  quotients of the magmatic operad by one relation of degree $3$ by
  studying their Hilbert series and providing combinarotial realizations.
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We study quotients of the magmatic operad, that is the free
  nonsymmetric operad over one binary generator. In the linear setting,
  we show that the set of these quotients admits a lattice structure and
  we show an analog of the Grassmann formula for the dimensions of these
  operads. In the nonlinear setting, we define comb associative operads,
  that are operads indexed by nonnegative integers generalizing the
  associative operad. We show that the set of comb associative operads
  admits a lattice structure, isomorphic to the lattice of nonnegative
  integers equipped with the division order, and we provide a finite
  convergent presentation for the comb associative operad in
  correspondence with $3$. Finally, we study quotients of the magmatic
  operad by one relation of degree three by studying their Hilbert
  series and providing combinatorial realizations.
\end{abstract}
